Real-time Attention Assessment for Social Robots

### 2015-09-01 paper.tex
Fixed comments

Engagement describes a cognitive, affective (specifically intrinsic motivation), and behavioral state of interaction with a computer application that ``makes the user want to be there" \cite{OBrien:2010}. Engaging interactions were thought to involve attention, intrinsic interest, interactivity, perceived control and choice, functionality and motivation.

In this way, in situ Visual Focus of Attention (VFOA) estimation is advantageous to human-robot interaction and a major contribution towards a better understanding of the interaction quality.\cite{yarbus1967eye, barber1976perception} suggest that human's interest is highly correlated with what they look at and the existing relationship between gaze and attention during social interaction has been exposed in~\cite{argyle1969social}.\fxfatal{This paragraph is not well connected to the previous ones}

@@

Education and learning environments are interesting application fields for research on attention assessment, since sustaining children's engagement over time is a key variable to ensure
effective learning (see for instance~\cite{Umbach}), and they indeed motivate this research. Besides, while~\cite{zhao2012learning} recommends the development of a teachable agent that is actively, rather than passively, engaged in the learning by teaching interaction, the increased learning gain results attained in~\cite{okita2006observation} were done so even with the pupil being taught having been instructed to not contribute much information. This suggests that it may not be necessary, from a learning by teaching point of view, for the teachable agent to participate actively in the interaction to incite educational benefits. However, from an engagement point of view, this may not necessarily be true.\fxfatal{rephrase, and be careful: 'learning by teaching' is only introduced in the next paragraph}

In fact, the use of robots in education comes with the potential to engage the child in meta-cognition through the learning by teaching paradigm, wherein a student takes the role of a teacher and experiences stronger educational benefits as a result (such as in \cite{Palinscar1984}).\fxnote{to be merged with previous paragraph?}

@@

In this research, we address the problem of tracking the children's engagement based on their VFOA and current performed task during a long term child-robot interaction in a learning context, first. And second, we provide qualitative and quantitative evaluation of the outcome provided using a first person RGB sensor approach. Moreover, this monitoring activity has been supporting our research in child-robot interaction for learning and instruction purposes.
\vfill

>>>>

Engagement describes a cognitive, affective (specifically intrinsic motivation), and behavioral state of interaction with a computer application that ``makes the user want to be there" \cite{OBrien:2010}. Engaging interactions were thought to involve intrinsic interest, interactivity, perceived control and choice, functionality, motivation and attention. In fact, \cite{yarbus1967eye,barber1976perception} suggest that human's attention is highly correlated with what they look at, and the existing relationship between gaze and attention during social interaction has been exposed in~\cite{argyle1969social}. In this way, in situ Visual Focus of Attention (VFOA) estimation is advantageous to human-robot interaction and a major contribution towards a better understanding of the interaction quality.

@@

Education and learning environments are interesting application fields for research on attention assessment, since sustaining children's engagement over time is a key variable to ensure effective learning (see for instance~\cite{Umbach}), and they indeed motivate this research. In fact, the use of robots in education comes with the potential to engage the child in meta-cognition through the learning by teaching paradigm, wherein a student takes the role of a teacher and experiences stronger educational benefits as a result (such as in \cite{Palinscar1984}).

While~\cite{zhao2012learning} recommends the development of a teachable agent that is actively, rather than passively, engaged in the learning by teaching interaction, the increased learning gain results attained in~\cite{okita2006observation} were done so even with the pupil being taught having been instructed to not contribute much information. This suggests that it may not be necessary, from a learning by teaching point of view, for the teachable agent to participate actively in the interaction to incite educational benefits. However, from an engagement point of view, this may not necessarily be true.

@@

In this research, we address the problem of tracking the children's engagement based on their VFOA and current performed task during a long term child-robot interaction in a learning context, first. And second, we provide qualitative and quantitative evaluation of the outcome provided using a first person RGB sensor approach. Moreover, this monitoring activity has been supporting our research in child-robot interaction for learning and instruction purposes.
